% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Sizhe Wei}

\basicInfo{
  \email{sizhewei@sjtu.edu.cn} \textperiodcentered\ 
  \homepage[Homepage]{http://sizhewei.github.io} \textperiodcentered\ 
  \github[SizheWei]{https://github.com/SizheWei}}
\basicInfo{\href{}{No.800,Dongchuan Road,Minhang District,Shanghai 200240, China}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{\href{http://en.sjtu.edu.cn/}{Shanghai Jiao Tong University (SJTU), Shanghai, China}}}{2017 -- Present}
\textit{Bachelor of Engineering} in \href{http://ee.sjtu.edu.cn/EN/Default.aspx}{Dept. Electronic Engineering}.\\
School of Electronic Information and Electrical Engineering, expected May 2021\\
Zhiyuan Honors Program of Engineering (An elite program for Top 5\% students).\\
Overall G.P.A.\quad  3.68 / 4.3 \quad | \quad 85.2 / 100

\section{\faStar\ Interests}
Explainable Artificial Intelligence(XAI), Machin Learning, Computer Vision.\\
Adept at coding and solving challenging problems, and open to exploring other interesting fields in AI.

\section{\faUsers\ Experience}
\datedsubsection{\textbf{SJTU Vision and Learning Lab}}{Dec. 2018 -- Present}
\role{Reseaarch Assistant}{Under the supervision of Prof. Bingbing Ni}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

\datedsubsection{\textbf{System and Network group, National University of Singapore}}{Jun. 2019 -- Present}
\role{Internship student}{Under the supervision of \href{https://www.comp.nus.edu.sg/~hebs/}{Prof. Bingsheng He}}
% Brief introduction: xxx
\begin{itemize}
  \item We built a demo about XAI applying for credit fraud detection based on SHAP and LIME. This demo can show the importance of the connection between features values user-entered and the classifications.
  \item We proposed our own thoughts about how to explain decisions offered by AI and we implemented it in code.
\end{itemize}

% \datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
% \role{\LaTeX, Maintainer}{Individual Projects}
% An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
% \begin{itemize}
%   \item Easy to be further customized or extended
%   \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
%   \item FontAwesome 4.5.0 support
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


\section{\faBook\ Coursework}
\textbf{Mathematics Foundation: }Mathematical Analysis, Linear Algebraic, Discrete Mathematics, Probability and Statistics\\
\textbf{Programming Foundation: }Thought and Method of Programming, Data Structures and Algorithms, Hardware language description\\
\textbf{Professional Courses: }Machine Learning, Simulation Electronic Technology, Signal and System


\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Coding: Python C++ MATLAB VHDL C LaTeX 
  \item Languages: English, Mandarin - Native speaker
  \item Diligent and highly self-motivated
\end{itemize}

\section{\faInfo\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Meritorious Winner of 2018 Interdisciplinary Contest In Modeling (Problem D)}{2018}
\datedline{Zhiyuan Honor Scholarship award for academic performance (Top 5\%)}{2017\&2018}
\datedline{The Third Prize Scholarship of SJTU (Top 20\%)}{2018}

\section{\faHeart\ Activities and Hobbies}
\begin{itemize}[parsep=0.5ex]
  \item SJTU Chu Cai Program member (Top 45 students of Class 2021)
  \item SJTU Baidu club member
  \item Zhiyuan college basketball team member
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
